\textbf{Discovery of a disrupting open cluster in the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream}

### 2018-11-04 ms.tex
refs

% \title{A young star cluster in the Galactic halo: \\
% Recent star formation associated with the Leading Arm of the Magellanic stream}
\title{\textbf{Discovery of a disrupting open cluster in the Galactic halo:\\
       a recent star formation event in the leading arm of the Magellanic stream}}

@@

We infer the mean proper motion of \clustername\ by constructing a probabilistic model of the cluster and background populations using astrometric data from \gaia.
We start by selecting all stars with $(\bprp)_0 < 0.35$ to remove low-mass and old main sequence star contamination in the region.
\figurename~\ref{fig:pm-members}, left (grey points), shows the sky positions of stars that pass this blue cut in the region around the young cluster.
The larger solid-line circle indicates the region we define as the cluster area, and the two smaller dashed-line circles indicate control fields that are combined and used for modeling the background distribution of proper motions.
The control fields are designed to, together, have the same total area as the cluster field.
The right panel of \figurename~\ref{fig:pm-members} shows the difference of the 2D proper motion distributions in the cluster and summed control fields.
The distinct over-density of stars near $(\mu_\alpha, \mu_\delta) \approx (-0.5, 0.5)~\masyr$\footnote{Throughout this article, we use $\mu_\alpha$ to refer to the proper motion value provided by \gaia, which includes the $\cos\delta$ term.} is the identified comoving association of blue stars.
Note that \figurename~\ref{fig:pm-members} is only meant an illustration: The cluster proper motion is determined probabilistically by taking into account the full \gaia\ covariance matrices for each source, as described below.

To measure the mean cluster proper motion, $\bs{\mu} = (\mu_\alpha, \mu_\delta)$, we first construct a model for the error-deconvolved proper motion distribution in the control fields using ``extreme deconvolution'' \citep[XD;][]{Bovy:2011} with two Gaussian components, which takes into account the full error distributions for each proper motion measurement (i.e. including covariances), $\mat{C}_\mu$, provided by \gaia\ \DR{2}.
After running XD, we fix the parameters of the background model and model the proper motion distribution in the cluster region using a two-component mixture model with a single, isotropic Gaussian component for the error-deconvolved cluster distribution with mean $\bs{x}$ and isotropic variance $s^2$, and the XD-inferred model for the control field, $p_{\textrm{XD}}$, for the background component.
In detail, taking $f$ to be the fraction of blue stars in this region belonging to the young cluster, and \truepm\ to be the true proper motion for a single star,
\begin{align}
    p(\bs{\mu} \given \truepm, \mat{C}_\mu) &=
        \norm(\bs{\mu} \given \truepm, \mat{C}_\mu)\\
    p(\truepm \given f, \bs{x}, s) &=
        f \, p_{\textrm{cl}}(\truepm \given \bs{x}, s)
        + (1-f) \, p_{\textrm{XD}}(\truepm)\\
    p_{\textrm{cl}}(\truepm \given \bs{x}, s) &=
        \norm(\truepm \given \bs{x}, s^2 \, \mathbb{I})
\end{align}
where $\norm(\bs{y} \given \bs{x}, \mat{C})$ represents the multidimensional normal distribution with mean $\bs{x}$ and covariance matrix $\mat{C}$, and $\mathbb{I}$ is the identity matrix.
Because all distributions are Gaussian, the per-star parameters (the true proper motions, \truepm) can be analytically marginalized out so that the per-star likelihood can be expressed as $p(\bs{\mu} \given f, \bs{x}, s, \mat{C}_\mu)$.
We assume that the measurements for each star, $n$, are independent so that the full likelihood of all $N$ stars given the parameters $(f, \bs{x}, s)$ is
\begin{align}
    p(\{\bs{\mu}_n\}_N \given \given f, \bs{x}, s, \{\mat{C}_{\mu, n}\}_N) &=
        \prod_n^N p(\bs{\mu}_n \given f, \bs{x}, s, \mat{C}_{\mu, n}) \quad .
        \label{eq:likelihood}
\end{align}

We use an ensemble Markov chain Monte Carlo (MCMC) sampler \citep[\texttt{emcee};][]{Goodman:2010, emcee} to generate posterior samples over the parameters $(f, \bs{x}, s)$ using the likelihood defined above (\equationname~\ref{eq:likelihood}), and assuming the following prior probability distributions: uniform over the domain $(-5, 5)~\masyr$ for each component of $\bs{x}$, uniform in $f$, and uniform in log-$s$ over the domain $-6 < \ln s < 4$ (with $s$ in units of \masyr).
We run the sampler with 32 walkers for 256 steps as burn-in, then reset the sampler and run for an additional 512 steps.
We then thin the resulting chains by taking every 16th sample, leaving a total of 1024 samples; We use these samples to estimate the median posterior parameter values and uncertainties,
For the young cluster, we find $\bs{m} = (-0.56,  0.47) \pm (0.04, 0.02)~\masyr$, $\ln s = -3.8 \pm 0.9$, and $f = 0.14 \pm 0.02$.
The proper-motion dispersion is consistent with zero, so is likely unmeasured; 95\% of the posterior samples have $s < 0.09~\masyr$.

@@

The deeper photometry from \decam\ provides a clear view of the stellar population of \clustername\ down to stellar masses $M \sim 0.9~\msun$:
\figurename~\ref{fig:decam-cmd} shows the \decam\ $g$ and $i$ band color-magnitude diagrams for control fields (left) and cluster fields (right) selected from the \decam\ footprint, once again showing the young main sequence (single stellar population in right panel).
We use the $g$- and $i$-band photometry for individual stars in a sub-section of the cluster field CMD (red dashed outlined region in \figurename~\ref{fig:decam-cmd}) to infer the stellar population parameters of \clustername.
To summarize our methodology, we generate posterior samplings over the stellar parameters of each individual source under an interim prior (over age, stellar mass, distance, etc.), then use these individual samplings to construct a Bayesian hierarchical model for a two-component mixture of a single stellar population and a background population.
The results of this modeling are presented in \sectionname~\ref{sec:popchars}.

In detail, we start by using the \texttt{isochrones} package \citep{Morton:2015} to generate posterior samplings over stellar parameters for each individual source given its photometry and an interim prior.
We use the \acronym{MIST} \citep{Choi:2016} isochrone library, and \texttt{isochrones} automatically performs interpolation between the provided grid of stellar isochrones to evaluate predicted stellar parameters at a given location in the CMD.
The stellar parameters for each source are its ``equal evolutionary point'' number $\eep$ (see \acronym{MIST} documentation\footnote{\url{http://waps.cfa.harvard.edu/MIST/}}), age $\tau$, metallicity $\feh$, extinction $A_V$, and distance $D$, which can be uniquely mapped to a point in the observed CMD;
The likelihood of a given set of these parameters, $\bs{\theta} = (\eep, \tau, \feh, A_V, D)$, is then computed from the photometry and (assumed Gaussian) photometric uncertainties given the predicted photometry.

@@

As expected, we find that the photometry for individual sources in the lower main sequence are very poorly constrained in all parameters, and the prior tends to pull the posterior samplings to prefer closer, older stellar parameters.
This is a weakness of our methodology for performing the hierarchical inference: each source is considered independently, even though there is clear structure in the CMD (i.e. \figurename~\ref{fig:decam-cmd}).
A more correct way to do this would be to infer the stellar parameters of \emph{all} stars, the cluster hyperparameters, and the background simultaneously.
However, for the \Nisofit\ stars we are using (in the red box in \figurename~\ref{fig:decam-cmd}), this model would have $\sim$2,000 free parameters, if left unmarginalized.
We are developing tools to perform star cluster parameter inference in this way (Morton et al., in prep.), but here we adopt a simple hack to allow us to instead perform individual posterior samplings and then combine into a hierarchical inference.

The brightest stars in the cluster have very precise \decam\ photometry, and have precise astrometry from \gaia, and therefore have membership probabilities from the previous section (\sectionname~\ref{sec:pmclean}).
Given their location in the CMD, these stars must be young, and so also have much better constrained stellar parameters.
We therefore use the brightest, high-probability \emph{kinematic} member --- XXX --- as an ``anchor'' star:
We model every other source (i.e. excluding XXX) in the \decam\ selection region by fitting the photometry of it and the anchor star simultaneously, assuming they have the same age, metallicity, distance, and extinction but different \eep\ values.
Motivated by the possible signature of an (unresolved) binary sequence in the \decam\ CMD, we add one further piece of complexity to the model by allowing the photometry of each non-anchor source to be fit as an unresolved binary star system.
This adds an additional parameter, the unresolved binary mass ratio $q$, to the list of inferred stellar parameters for each source.
The details of this model are handled by the \texttt{isochrones} package.

\begin{table}[ht]
\begin{center}
    \begin{tabular}{ c | c | c }
        \toprule
        Parameter & Prior & Bounds \\
        \toprule
        $\eep$ & uniform & $(202, 355)$ \\
        $\tau$ & uniform & $(10~\textrm{Myr}, 15~\textrm{Gyr})$ \\
        $\feh$ & uniform & $(-2, 0.5)$ \\
        $A_V$ & $\propto A_V^{-1}$ & $(0.001, 1)~\textrm{mag}$ \\
        $D$ & $\propto D^{2}$ & $(1, 100)~\kpc$ \\
        \toprule
    \end{tabular}
\caption{Prior probability distributions for each of the stellar parameters defined in \sectionname~\ref{sec:popmodel}.
\label{tbl:priors}}
\end{center}
\end{table}

Ultimately we generate posterior samplings over the parameters $(\bs{\theta}, q)$ for each of the \Nisofit\ sources in the selected region of the \decam\ CMD using \texttt{PyMultinest} \citep{TODO}, and store the value of the prior evaluated at the location of each sample.
We then use these samples and interim prior values to construct our hierarchical model, as described below.
In the hierarchical model, we assume that the stellar parameters of each primary star in the selected region are either drawn from the cluster, or a background (stellar halo) population.
For the cluster, we assume the values are drawn from delta functions in age, metallicity, distance, and extinction, with the centroids of the delta functions $\bs{\alpha} = (\tau^*, \feh^*, D^*, A_V^*)$ as hyperparameters of the hierarchical inference.
For the background model, we assume the same priors as specified in \tablename~\ref{tbl:priors}.
The one additional parameter that must be included in this hierarchical model is the ``mixture weight'': the global fraction of sources that are likely cluster members, $f$.
To compute the likelihood of the hierarchical model, we use the individual posterior samplings to marginalize over the per-source $k$ stellar parameters $\bs{\theta}_k$ to compute the marginal likelihood $p(\bs{m}_k \given \bs{\alpha}, f)$, where $\bs{m}_k = (g, i)_k$ is the vector of photometric data;
This likelihood for a single source $k$ given a set of hyperparameters $(\bs{\alpha}, f)$ is
\begin{equation}
    p(\bs{m}_k \given \bs{\alpha}, f) = \int \dd \bs{\theta}_k \,
        p(\bs{m}_k \given \bs{\theta}_k) \,
        p(\bs{\theta}_k \given \bs{\alpha}, f) \quad .
\end{equation}
We employ the ``importance sampling trick'' (see, e.g., Appendix of \citealt{Price-Whelan:2018} or \citealt{Hogg:2010, Foreman-Mackey:2014} for other examples) to re-write an approximate form for this marginal likelihood as
\begin{equation}
    p(\bs{m}_k \given \bs{\alpha}, f) \approx \frac{\mathcal{Z}_k}{J} \,
        \sum_j^J \frac{p(\bs{\theta}_{kj} \given \bs{\alpha}, f)}{p(\bs{\theta}_{kj} \given \bs{\alpha}_0, f)}
        \label{eq:marglike}
\end{equation}
where the index $j$ specifies the index of one of $J$ posterior samples generated from the independent samplings (described above), $\mathcal{Z}_k$ is a constant, and the denominator, $p(\bs{\theta}_{kj} \given \bs{\alpha}_0, f)$, are the values of the interim prior used to do the independent samplings.
In this work, $K=\Nisofit$ and we adopt $J=2048$.

\todo{we ignore the $q$!}
With the marginal likelihood (\equationname~\ref{eq:marglike}), we then need to specify prior probability distributions for the hyperparameters $(\bs{\alpha}, f)$, and we can then generate posterior samples for the hyperparameters;
We use uniform priors for all of these, as summarized in \tablename~\ref{tbl:hyperpriors}.
We then use \texttt{emcee} \citep{Goodman:2010, emcee} to sample from the posterior probability distribution for the hyperparameters given all of the photometric data,
\begin{equation}
    p(\bs{\alpha}, f \given \{\bs{m}_k\}) \propto
        p(\bs{\alpha}) \, p(f) \,
        \prod_k^K p(\bs{m}_k \given \bs{\alpha}, f) \quad .
\end{equation}
Here we use 64 walkers and run for an initial 128 steps to burn-in the sampler before running for a final 1024 steps.
\figurename~\ref{fig:hierarch-corner} shows a corner plot showing all 1D and 2D marginal posterior probability distributions estimated from the samples.

@@

We use the posterior samples from the hierarchical inference described in \sectionname~\ref{sec:popmodel} to compute the posterior probabilities that each source in the \decam\ CMD selection box (red box, \figurename~\ref{fig:decam-cmd}) is a member of the cluster.
\figurename~\ref{fig:hierarch-iso} shows the \decam\ photometry for all sources with membership probability $> 0.5$ (circle markers).
Over-plotted in \figurename~\ref{fig:hierarch-iso} (blue, solid line) is a \acronym{MIST} isochrone with median posterior parameters derived from the hierarchical modeling, shifted to the median distance and extincted given the median $A_V$ value.
We find that \clustername\ is indeed young, distant, and metal poor, with median posterior values of age $\tau \approx \clage$, distance $D \approx \cldist$, and metallicity $\feh \approx \clfeh$.
Also plotted is the equal-mass binary sequence (green, dashed line) computed from the median posterior sample, highlighting that the cluster may contain a significant number of binary or multiple star systems.

We use the isochrone corresponding to the median posterior sample to estimate the total stellar mass of the cluster.
By assuming that the \decam\ imaging is 100\% complete to stars with $(g-i) < 0.3)$ and $g < 22$, and by assuming a Kroupa initial mass function \citep{Kroupa:TODO}, we use the number of observed stars and the isochrone to compute the total mass, $M_{\rm tot, *} \approx 1200~\msun$.

@@

At the sky location and distance of \clustername, i.e. well into the Galactic halo, the only plausible gas reservoirs that could have formed a young cluster are the Magellanic stream, or a previously unknown high velocity cloud (HVC).
HVCs are thought to either be accreted and therefore lower metallicity than typical present-day Milky Way gas, or ejected from the Milky Way through a ``Galactic fountain''-like process and therefore comparable metallicity to disk gas.
Both processes clearly occur: the Magellanic stream itself is evidence of gas accretion in to the Milky Way halo, and the well-known Smith Cloud \citep{TODO} is a metal-rich ($\feh \sim 0.5$) HVC that could have originated from the Galactic disk \citep{TODO}.
Given the low metallicity of the stars in \clustername, the gas it formed from was likely extragalactic, as any violent star-forming regions in the Milky Way disk that could have driven gas out into the halo have, at present-day, significantly higher metallicity than this cluster.

Here we take a closer look at the \hi gas in the vicinity of \clustername.
\figurename~\ref{fig:XXXX} shows the \hi column density in the region around the leading arm of the Magellanic stream, with the location of \clustername\ marked.
While no bulk metallicity measurements exist for the LA gas, \todo{...recent measurements suggest comparable to SMC?} \citep{Fox:2018}.
Given its extragalactic origin, its proximity to the Magellanic stream suggests that \clustername\ could have formed from this gas.
Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu:2014, MoniBidin:2017}, however, this is the first time that an entire star cluster has been detected so far from the Clouds.

@@

\software{
    \package{Astropy} \citep{astropy, astropy:2018},
    \package{dustmaps} \citep{dustmaps},
    \package{emcee} \citep{emcee, emcee:ascl},
    \package{gala} \citep{gala},
    \package{IPython} \citep{ipython},
    \package{matplotlib} \citep{mpl},
    \package{numpy} \citep{numpy},
    \package{schwimmbad} \citep{schwimmbad},
    \package{scipy} \citep{scipy}
}

>>>>

% \title{A young star cluster in the Galactic halo: \\
% Recent star formation associated with the Leading Arm of the Magellanic stream}
\title{\textbf{Discovery of a disrupting open cluster in the Milky Way halo:\\
       a recent star formation event in the leading arm of the Magellanic stream}}

@@

We infer the mean proper motion of \clustername\ by constructing a probabilistic model of the cluster and background populations using astrometric data from \gaia.
We start by selecting all stars with $(\bprp)_0 < 0.35$ to remove low-mass and old main sequence star contamination in the region.
\figurename~\ref{fig:pm-members}, left (grey points), shows the sky positions of stars that pass this blue cut in the region around the young cluster.
The larger solid-line circle indicates the region we define as the cluster area, and the two smaller dashed-line circles indicate control fields that are combined and used for modeling the background distribution of proper motions.
The control fields are designed to, together, have the same total area as the cluster field.
The right panel of \figurename~\ref{fig:pm-members} shows the difference of the 2D proper motion distributions in the cluster and summed control fields.
The distinct over-density of stars near $(\mu_\alpha, \mu_\delta) \approx (-0.5, 0.5)~\masyr$ is the identified comoving association of blue stars.\footnote{Throughout this article, we use $\mu_\alpha$ to refer to the proper motion value provided by \gaia, which includes the $\cos\delta$ term.}
Note that \figurename~\ref{fig:pm-members} is only meant an illustration: The cluster proper motion is determined probabilistically by taking into account the full \gaia\ covariance matrices for each source, as described below.

To measure the cluster (mean) proper motion, we first construct a model for the error-deconvolved proper motion distribution in the control fields using ``extreme deconvolution'' \citep[XD;][]{Bovy:2011} with two Gaussian components. XD takes into account the full error distributions for each proper motion measurement $\bs{\mu} = (\mu_\alpha, \mu_\delta)$, including covariances $\mat{C}_\mu$, provided by \gaia\ \DR{2}.
After running XD, we fix the parameters of the background model and model the proper motion distribution in the cluster region using a two-component mixture model with a single, isotropic Gaussian component for the error-deconvolved cluster distribution with mean $\bs{x}$ and isotropic variance $s^2$, and the XD-inferred model for the control field, $p_{\textrm{XD}}$, for the background component.
In detail, taking $f$ to be the fraction of blue stars in this region belonging to the young cluster, and \truepm\ to be the true proper motion for a single star,
\begin{align}
    p(\bs{\mu} \given \truepm, \mat{C}_\mu) &=
        \norm(\bs{\mu} \given \truepm, \mat{C}_\mu)\\
    p(\truepm \given f, \bs{x}, s) &=
        f \, p_{\textrm{cl}}(\truepm \given \bs{x}, s)
        + (1-f) \, p_{\textrm{XD}}(\truepm)\\
    p_{\textrm{cl}}(\truepm \given \bs{x}, s) &=
        \norm(\truepm \given \bs{x}, s^2 \, \mathbb{I})
\end{align}
where $\norm(\cdot \given \bs{y}, \mat{C})$ represents the multidimensional normal distribution with mean $\bs{y}$ and covariance matrix $\mat{C}$, and $\mathbb{I}$ is the identity matrix.
Because all distributions are Gaussian, the per-star parameters (the true proper motions, \truepm) can be analytically marginalized out so that the per-star likelihood can be expressed as $p(\bs{\mu} \given f, \bs{x}, s, \mat{C}_\mu)$.
We assume that the measurements for each star, $n$, are independent so that the full likelihood of all $N$ stars given the parameters $(f, \bs{x}, s)$ is
\begin{align}
    p(\{\bs{\mu}_n\}_N \given f, \bs{x}, s, \{\mat{C}_{\mu, n}\}_N) &=
        \prod_n^N p(\bs{\mu}_n \given f, \bs{x}, s, \mat{C}_{\mu, n}) \quad .
        \label{eq:likelihood}
\end{align}

We use an ensemble Markov chain Monte Carlo (MCMC) sampler \citep[\texttt{emcee};][]{emcee, Goodman:2010} to generate posterior samples over the parameters $(f, \bs{x}, s)$ using the likelihood defined above (\equationname~\ref{eq:likelihood}), and assuming the following prior probability distributions: uniform over the domain $(-5, 5)~\masyr$ for each component of $\bs{x}$, uniform in $f$, and uniform in log-$s$ over the domain $-6 < \ln s < 4$ (with $s$ in units of \masyr).
We run the sampler with 32 walkers for 256 steps as burn-in, then reset the sampler and run for an additional 512 steps.
We then thin the resulting chains by taking every 16th sample, leaving a total of 1024 samples; We use these samples to estimate the median posterior parameter values and uncertainties,
For the young cluster, we find $\bs{x} = (-0.56,  0.47) \pm (0.04, 0.02)~\masyr$, $\ln s = -3.8 \pm 0.9$, and $f = 0.14 \pm 0.02$.
The proper-motion dispersion is consistent with zero, and is likely unmeasured; 95\% of the posterior samples have $s < 0.09~\masyr$.

@@

While the \gaia\ data provide exquisite astrometric data for the brightest members of \clustername, constraints on the stellar population from the \gaia\ data alone are limited by degeneracies in the mapping from the color-magnitude diagram to stellar parameters.
To measure the cluster population parameters, we therefore use the deeper photometry from \decam, which provides a clear view of the main sequence of \clustername\ down to stellar masses $M \sim 0.9~\msun$.
\figurename~\ref{fig:decam-cmd} shows the \decam\ $g$ and $i$ band color-magnitude diagrams for control fields (left) and cluster fields (right) selected from the \decam\ footprint, once again showing the young main sequence (coherent stellar population in right panel).
We use the $g$- and $i$-band photometry for individual stars in a sub-section of the cluster field CMD (red dashed outlined region in \figurename~\ref{fig:decam-cmd}) to infer the stellar population parameters of \clustername.
To summarize our methodology, we first generate independent posterior samplings over the stellar parameters of each individual source under an interim prior (over age, stellar mass, distance, etc.), then use these individual samplings to construct a Bayesian hierarchical model for a two-component mixture model of the cluster and a background population.
If you prefer to skip the details, the results of this modeling are presented in \sectionname~\ref{sec:popchars}.

In detail, we start by using the \texttt{isochrones} package \citep{Morton:2015} to generate posterior samplings over stellar parameters for each individual source given its photometry and an interim prior.
We use the \acronym{MIST} \citep{Dotter:2016, Choi:2016, Paxton:2011, Paxton:2013, Paxton:2015} isochrone grid, and \texttt{isochrones} automatically performs interpolation between the provided grid of stellar isochrones to predict photometry given a set of stellar parameters.
Here, the stellar parameters for each source are its ``equal evolutionary point'' number $\eep$ (see \acronym{MIST} documentation\footnote{\url{http://waps.cfa.harvard.edu/MIST/}}), age $\tau$, metallicity $\feh$, extinction $A_V$, and distance $D$, which can be uniquely mapped to a point in the observed CMD;
The likelihood of a given set of these parameters, $\bs{\theta} = (\eep, \tau, \feh, A_V, D)$, is then computed from the photometry and (assumed Gaussian) photometric uncertainties given the predicted photometry.

@@

\begin{table}[ht!]
\begin{center}
    \begin{tabular}{ c | c | c }
        \toprule
        Parameter & Prior & Bounds \\
        \toprule
        $\eep$ & uniform & $(202, 355)$ \\
        $\tau$ & uniform & $(10~\textrm{Myr}, 15~\textrm{Gyr})$ \\
        $\feh$ & uniform & $(-2, 0.5)$ \\
        $A_V$ & $\propto A_V^{-1}$ & $(0.001, 1)~\textrm{mag}$ \\
        $D$ & $\propto D^{2}$ & $(1, 100)~\kpc$ \\
        \toprule
    \end{tabular}
\caption{Prior probability distributions for each of the stellar parameters defined in \sectionname~\ref{sec:popmodel}.
\label{tbl:priors}}
\end{center}
\end{table}

We find that the photometry for individual sources in the lower main sequence are very poorly constrained in all parameters, and the prior tends to pull the posterior samplings to prefer closer, older stellar parameters.
This is a weakness of our methodology for performing the hierarchical inference: Each source is considered independently, even though there is clear structure in the CMD (i.e. \figurename~\ref{fig:decam-cmd}), and inferring isochronal parameters for individual lower main sequence stars is a fundamentally degenerate problem.
A more correct way to do this would be to infer the stellar parameters of \emph{all} stars, the cluster hyperparameters, and the background simultaneously.
However, for the \Nisofit\ stars we are using (in the red box in \figurename~\ref{fig:decam-cmd}), this model would have $\sim$2,000 free parameters if left unmarginalized.
We are developing tools to perform star cluster parameter inference in this way (Morton et al., in prep.), but here we adopt a simple hack to allow us to instead perform individual posterior samplings and then combine those samplings into a hierarchical inference.

The brightest stars in the cluster have very precise \decam\ photometry, and have precise astrometry from \gaia.
Given their location in the CMD, these stars must be young, and so also have much better constrained stellar parameters.
We therefore use the brightest \emph{kinematic} member of \clustername\ as an ``anchor'' star:
We model every other source in the \decam\ selection region (i.e. excluding this one) by fitting the photometry of it and the anchor star simultaneously, assuming they have the same age, metallicity, distance, and extinction but different \eep\ values.
Motivated by the possible signature of an (unresolved) binary sequence in the \decam\ CMD, we add one further piece of complexity to the model by allowing the photometry of each non-anchor source to be fit as an unresolved binary star system.
This adds an additional parameter, the unresolved binary mass ratio $q$, to the list of inferred stellar parameters for each source, but, for this work, we ignore the binary companions and implicitly marginalize over $q$ in what follows.
The details of this model are handled by the \texttt{isochrones} package.

We generate posterior samplings over the parameters $(\bs{\theta}, q)$ for each of the \Nisofit\ sources in the selected region of the \decam\ CMD using \texttt{PyMultinest} \citep{Buchner:2014, Feroz:2008, Feroz:2009}, and store the value of the prior evaluated at the location of each sample.
We then use these samples and interim prior values to construct our hierarchical model, as described below.

In the hierarchical model, we assume that the stellar parameters of each primary star in the selected region are either drawn from the cluster, or a background (stellar halo) population.
For the cluster, we assume that the values are drawn from delta functions in age, metallicity, distance, and extinction, with the centroids of the delta functions $\bs{\alpha} = (\tau^*, \feh^*, D^*, A_V^*)$ as hyperparameters of the hierarchical inference.
For the background model, we assume the same priors as specified in \tablename~\ref{tbl:priors}.
The one additional parameter that must be included in this hierarchical model is the mixture weight: The global fraction of sources that are likely cluster members, $f$.
To compute the likelihood for the hierarchical model, we use the individual posterior samplings to marginalize over the per-source stellar parameters $\bs{\theta}_n$ to compute the marginal likelihood $p(\bs{m}_n \given \bs{\alpha}, f)$, where $\bs{m}_n = (g, i)_n$ is the vector of photometric data for source $n$;
This likelihood for a single source given a set of hyperparameters $(\bs{\alpha}, f)$ is then
\begin{equation}
    p(\bs{m}_n \given \bs{\alpha}, f) = \int \dd \bs{\theta}_n \,
        p(\bs{m}_n \given \bs{\theta}_n) \,
        p(\bs{\theta}_n \given \bs{\alpha}, f) \quad .
\end{equation}
We employ the ``importance sampling trick'' (see, e.g., Appendix of \citealt{Price-Whelan:2018} or \citealt{Hogg:2010, Foreman-Mackey:2014} for other examples) to re-write an approximate form for this marginal likelihood as
\begin{equation}
    p(\bs{m}_n \given \bs{\alpha}, f) \approx \frac{\mathcal{Z}_n}{K} \,
        \sum_k^K \frac{p(\bs{\theta}_{nk} \given \bs{\alpha}, f)}{p(\bs{\theta}_{nk} \given \bs{\alpha}_0, f)}
        \label{eq:marglike}
\end{equation}
where the index $k$ specifies the index of one of $K$ posterior samples generated from the independent samplings (described above), $\mathcal{Z}_n$ is a constant, and the denominator, $p(\bs{\theta}_{nk} \given \bs{\alpha}_0, f)$, are the values of the interim prior used to do the independent samplings.
In this work, $N=\Nisofit$ and we adopt $K=2048$.

With the marginal likelihood (\equationname~\ref{eq:marglike}), we then need to specify prior probability distributions for the hyperparameters $(\bs{\alpha}, f)$, and we can then generate posterior samples for the hyperparameters.
We use uniform priors for all of these, as summarized in \tablename~\ref{tbl:hyperpriors}.
We use \texttt{emcee} \citep{emcee, Goodman:2010} to sample from the posterior probability distribution for the hyperparameters given all of the photometric data,
\begin{equation}
    p(\bs{\alpha}, f \given \{\bs{m}_n\}) \propto
        p(\bs{\alpha}) \, p(f) \,
        \prod_n^N p(\bs{m}_n \given \bs{\alpha}, f) \quad .
\end{equation}
Here we use 64 walkers and run for an initial 128 steps to burn-in the sampler before running for a final 1024 steps.
\figurename~\ref{fig:hierarch-corner} shows a corner plot with all 1D and 2D marginal posterior probability distributions estimated from the samples.

@@

We use the posterior samples from the hierarchical inference described in \sectionname~\ref{sec:popmodel} to compute the posterior probabilities that each source in the \decam\ CMD selection box (red box, \figurename~\ref{fig:decam-cmd}) is a member of the cluster.
\figurename~\ref{fig:hierarch-iso} shows the \decam\ photometry for all sources with membership probability $> 0.5$ (circle markers).
Over-plotted in \figurename~\ref{fig:hierarch-iso} (blue, solid line) is a \acronym{MIST} isochrone with the median posterior parameters derived from the hierarchical modeling, shifted to the median distance and extincted given the median $A_V$ value.
We find that \clustername\ is indeed young, distant, and metal poor, with median posterior values of age $\tau \approx \clage$, distance $D \approx \cldist$, and metallicity $\feh \approx \clfeh$ (see also \tablename~\ref{tbl:clusterparams} for a summary).
Also plotted in \figurename~\ref{fig:hierarch-iso} is the equal-mass binary sequence (green, dashed line) computed from the median posterior sample: The abundance of sources between the nominal isochrone and the binary sequence highlights the fact that the cluster may contain a significant number of binary or multiple star systems, but we leave a detailed study of multiplicity to future work.

We use the isochrone corresponding to the median posterior sample to estimate the total stellar mass of the cluster.
By assuming that the \decam\ imaging is 100\% complete to stars with $(g-i) < 0.3)$ and $g < 22$, and by assuming a Kroupa initial mass function \citep{Kroupa:2001}, we use the number of observed stars and the isochrone to compute the total mass, $M_{\rm tot, *} \approx 1200~\msun$.

@@

At the sky location and distance of \clustername, i.e. well into the Galactic halo, the only plausible gas reservoirs that could have formed a young cluster are the Magellanic stream, or a previously unknown high velocity cloud (HVC).
HVCs are thought to either be accreted and therefore lower metallicity than typical present-day Milky Way gas, or ejected from the Milky Way through a ``Galactic fountain''-like process and therefore comparable metallicity to disk gas.
Both processes clearly occur: the Magellanic stream itself is evidence of gas accretion in to the Milky Way halo, and the well-known Smith Cloud \citep{Smith:1963} is a metal-rich \citep[$\feh \sim 0.5$[]{Fox:2016} HVC that plausibly originated from the Galactic disk \citep[e.g.,][]{Bregman:1980}.
Given the low metallicity of the stars in \clustername, the gas it formed from was likely extragalactic, as any violent star-forming regions in the Milky Way disk that could have driven gas so far out into the halo have, at present-day, significantly higher metallicity than this cluster.

% TODO: Nidever plots at different velocities?
Here we take a closer look at the \hi gas in the vicinity of \clustername.
\figurename~\ref{fig:XXXX} shows the \hi column density in the region around the leading arm of the Magellanic stream, with the location of \clustername\ marked.
While no bulk metallicity measurements exist for the LA gas, \todo{...recent measurements suggest comparable to SMC?} \citep{Fox:2018}.
Given its extragalactic origin, its proximity to the Magellanic stream suggests that \clustername\ could have formed from this gas.
Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu:2014, MoniBidin:2017}, however, this is the first time that an entire star cluster has been detected so far from the Clouds.

@@

\software{
    \package{Astropy} \citep{astropy, astropy:2018},
    \package{dustmaps} \citep{dustmaps},
    \package{emcee} \citep{emcee, emcee:ascl},
    \package{gala} \citep{gala},
    \package{IPython} \citep{ipython},
    \package{matplotlib} \citep{mpl},
    \package{numpy} \citep{numpy},
    \package{PyMultinest} \citep{Buchner:2014},
    \package{schwimmbad} \citep{schwimmbad},
    \package{scipy} \citep{scipy}
}
